\documentclass{article}
\usepackage[english]{babel}
\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

\usepackage{amsmath, amsfonts, amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{xspace}
\usepackage{gensymb}
\usepackage{float}
\usepackage{appendix}
\usepackage{caption}
\captionsetup[table]{skip=3pt}
\usepackage{wrapfig}
\setlength{\columnsep}{1.5em}
\usepackage{comment}

\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage[capitalize]{cleveref}
\usepackage{xr-hyper}

\crefname{figure}{fig.}{figs.}
\Crefname{figure}{Fig.}{Figs.}
\crefname{equation}{eq.}{eqs.}
\Crefname{equation}{Eq.}{Eqs.}
\crefname{table}{table}{tables}
\Crefname{table}{Table}{Tables}
\crefname{algorithm}{alg.}{algs.}
\Crefname{algorithm}{Alg.}{Algs.}
\usepackage{authblk}

% 定理環境
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{proposition}[theorem]{Proposition}

\renewcommand{\appendixpagename}{Supplementary Information}
\renewcommand{\appendixtocname}{Supplementary Information}

% カスタムコマンド（既存）
\input{commands}

% Reference
\usepackage{csquotes}
\usepackage[
    style=numeric-comp,
    backend=biber,
    sorting=none,
    date=year,natbib,
    maxnames=10,
    minnames=1,
    doi=true,
    url=true
]{biblatex}

\DeclareFieldFormat{labelnumberwidth}{#1.}
\DeclareFieldFormat{shorthandwidth}{#1.}
\setlength{\biblabelsep}{0.5em}

\addbibresource{citation_biophysj.bib}

\DeclareDelimFormat{finalnamedelim}{\addspace and\space}
\DeclareDelimFormat{multinamedelim}{\addcomma\space}

\AtEveryBibitem{
  \iffieldundef{doi}
    {}
    {\clearfield{url}}
}
\usepackage{fontspec}
\setmainfont{Helvetica}
\pagestyle{empty}

\externaldocument{biophysj}

\begin{document}

\begin{comment}
% ========== Title page ==========
\begin{titlepage}
\vspace*{2em}

% Main heading for SI
\noindent{\LARGE AFM-Fold: Rapid Reconstruction of Protein Conformations from AFM Images\par}

\vspace{2.5em}

% Authors
\noindent{\normalsize
\textit{Tsuyoshi Kawai}\textsuperscript{1},\;
\textit{Yasuhiro Matsunaga}\textsuperscript{*,1,2}\par}

\vspace{1.0em}

% Affiliations
{\small
\noindent\textsuperscript{1}Graduate School of Science and Engineering, Saitama University\par
\noindent\textsuperscript{2}RIKEN Center for Computational Science\par}

\vspace{1.0em}

% Corresponding authors (edit as needed)
\noindent{\small
\textit{* Corresponding author:} 
\href{mailto:ymatsunaga@riken.jp}{\underline{ymatsunaga@riken.jp}}\par}

\vspace{2.0em}

\noindent{\small\bfseries Supporting Materials\par}

\vfill

% Optional bottom line like the sample (“Supporting Materials”)
\end{titlepage}
% ========== End of title page ==========
\end{comment}

\input{sections/appendix}

\printbibliography

\end{document}
