\section*{Data availability}
The code of \Model is publicly available at \url{http://github.com/matsunagalab/afmfold}.
Notebooks, scripts, and datasets to reproduce the results of this paper are publicly available at Zenodo \url{https://zenodo.org/records/17597490} \cite{kawai_dataset_nodate}. 
HS-AFM data of \flhac are available upon reasonable request to the corresponding author and with the permission of the original authors \cite{inoue_structural_2019}. 

\section*{Author Contributions}
T. Kawai carried out the primary research, including conceptual development, data analysis, and manuscript drafting. 
Y. Matsunaga designed the overall research plan, provided continuous guidance, oversaw the progress of the work, and assisted in revising and contributed to the refinement of the manuscript.

\section*{Declaration of interests}
The authors declare that they have no competing interests.

\section*{Declaration of generative AI and AI-assisted technologies in the writing process}
Statement: During the preparation of this work the authors used ChatGPT in order to assist with language refinement and editing. 
After using this service, the authors reviewed and edited the content as needed and take full responsibility for the content of the publication.

\section*{Acknowledgements}
\label{sec:acknowledgements}
A preliminary version of this work, \url{https://www.biorxiv.org/content/10.1101/2025.11.17.688836v1} (DOI: \url{https://doi.org/10.1101/2025.11.17.688836}), was deposited in bioRxiv on November 17, 2025.
We appreciate Tohru Minamino (The University of Osaka) and Noriyuki Kodera (Kanazawa University) for kindly providing the experimental AFM image data used in this work. 
This work was supported by JSPS KAKENHI (Grant number: 23H03412), and partly supported by MEXT as "Program for Promoting Researches on the Supercomputer Fugaku" (Development and application of large-scale simulation-based inferences for biomolecules JPMXP1020230119) and used computational resources of supercomputer Fugaku provided by the RIKEN Center for Computational Science (Project IDs: hp230209, hp240215, hp250233). 
